Deployable Probabilistic Programming

### 2019-04-17 paper/paper.tex
cleanups

\paragraph{Data interface} The data for inference may come from
a variety of sources: network, databases, distributed file
systems, and in many different formats. Efficient inference
depends on fast data access and updating. Libraries for data
access and manipulation are available in the host environment.
While the host environment can be used as a proxy retrieving and
transforming the data, such as in the case of Stan~\cite{Stan17}
integrations, sometimes direct access from the probabilistic
code is the preferred option, for example when the data is
streamed or retrieved conditionally.

@@

>>>>

\paragraph{Data interface} The data for inference may come from
a variety of sources: network, databases, distributed file
systems, and in many different formats. Efficient inference
depends on fast data access and updating. Libraries for data
access and manipulation are available in the host environment.
While the host environment can be used as a proxy retrieving and
transforming the data, such as in the case of Stan~\cite{Stan17}
integrations, sometimes direct access from the probabilistic
code is the preferred option, for example when the data is
streamed or retrieved conditionally, as in active
learning~\cite{SLB15}.

@@

\cite{R16} \cite{KB15} \cite{N12} \cite{HG11} \cite{LN89}
